---
title: "Adjacency"
author: "redist_workshop"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

## Libraries

For these exercises, we only need a few packages. We'll use `redist` for a high-level adjacency function and data, `geomander` for some adjacency inspecting tools, and `sf` for lower-level shape tools.
```{r}
# library(here)
library(redist)
library(geomander)
library(sf)
```

## Data

We use the 99 Iowa counties here. In Iowa, congressional districts are drawn without splitting counties. Thus, these 99 counties are partitioned into 4 districts with nearly equal population.

The Iowa data can be loaded from `redist` with:

```{r}
data('iowa')
```

# Exercises

## 1. Constructing an adjacency graph

#### a.
Using `redist.adjacency()`, construct an adjacency graph for the Iowa data. This will be a _0-indexed Rook's adjacency list_.

```{r}

```


#### b.
The first entry should look like:

```markdown
[[1]]
[1]  1 14 38 60 87
```

Which counties are adjacent to Adair (`iowa$name[1]`) county?

```{r}

```


#### c.

This adjacency list describes an adjacency graph, which is the collection of nodes (counties) and edges (the connections between nodes). Plot it using `redist.plot.adj()`.

```{r}

```

#### d. 

How many edges are there in this graph? Recall that our adjacency list is just a symmetric list! (Feel free to skip this question and come back to it if you have time.)

```{r}

```

## 2. Queen's Contiguity

#### a.
Now, let's build a new adjacency graph that's Queen's contiguous. For this, we can use `st_touches()` from the `sf` package.

```{r}

```

#### b. 

The output here is a list, but it is a Sparce Geometry Binary Predicate (sgbp) list! That's fine, because we can treat it as a list anyway. It just prints a bit differently.

However, we do have one issue with this:

```markdown
1: 2, 5, 15, 25, 39, 61, 88
```
It's one indexed! Make it 0 indexed by subtracting 1 from each entry in the list.

```{r}

```

#### c.

Plot our queen's adjacency list using `redist.plot.adj()`.

```{r}

```

This makes a big difference for a weird state like Iowa, where early planning was aimed to have a county traversable by horse in a day. As a result, you have lots of square small counties which are adjacent to each other only at a single point.

## 3. Comparing Adjacencies

Visually, we saw the difference between the Rook's and Queen's adjacencies above. Let's dive a bit into how they're formally different.

#### a.

Using `geomander::compare_adjacencies()` compare the two.

```{r}

```

#### b.

What are the `relation`s between the differences in the adjacency graphs? This is a formalization of the spatial relationship between the shapes causing the difference.

```{r}

```


#### c. 

What are the `class`es between the differences in the adjacency graphs? This is the geographic intersection of the shapes that cause differences.

```{r}

```
