---
title: "redist_map"
author: "redist_workshop"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

## Libraries

For these exercises, we only need a few packages. We'll use `redist` again to unlock the `redist_map()`, `geomander` for data, and `sf` for some shape-focused tools.
```{r}
library(here)
library(redist)
library(geomander)
library(sf)
```


# Exercises

## 1.

You did this before, but let's make some practice!

#### a.

We will use some data from NJ now. This data is at the "VTD" level, which is the voting tabulation district. This is the Census Bureau's idea of voting precincts or voting wards.

We can access a version of this which combines Census data with a retabulation of [VEST Team](https://twitter.com/vest_team) data from the [ALARM Project](https://alarm-redist.github.io/posts/2021-08-10-census-2020/), using `geomander::get_alarm()`. Call this data `nj`

```{r}
nj <- get_alarm(state = 'NJ')
```


#### b.

Next, we need to read in the enacted districts. To read in shapes, we can use `sf::st_read()`.

Without needing to download the data, we read this directly from a link:
`https://redistricting.lls.edu/wp-content/uploads/nj_2020_congress_2021-12-22_2031-06-30.json`.

Call this data `nj_cd`.

```{r}
nj_cd <-st_read('https://redistricting.lls.edu/wp-content/uploads/nj_2020_congress_2021-12-22_2031-06-30.json')
```

#### c.

Now, we need to get district numbers from `nj_cd` matched to the VTDs in `nj`. To do this, we can use `geomander::geo_match()`.

```{r}
nj_match <- geo_match(from = nj, to = nj_cd)
```

This gives the numerical match from each VTD to each district.


#### d.

Add the district numbers to the `nj` as a new column called `cd_2020`. Beware, the output of `geo_match()` is in the order of the data, not the actual district numbers.

```{r}
unique(nj_cd$District)


nj <- nj %>% 
    mutate(cd_2020 = nj_cd$District[nj_match])
```


## 2.

Let's make our first `redist_map` using `nj`!

#### a.

Create an object `map_nj` using `redist_map()`. Set the `existing_plan` input as `cd_2020`.

```{r}
map_nj <- redist_map(nj, existing_plan = cd_2020)
```

```{r}

```


#### b.

What new column(s) were added to `map_nj`?

```{r}
colnames(map_nj)
```

#### c. 

Look at the new column(s) and describe them.

```{r}
map_nj$adj[[1]]
```

It's a zero-indexed adjacency list!

## 3.

Beyond a new column, the object is now a `redist_map`.

```{r}

```

#### a. 

What are the new `attributes()` in `map_nj`? 

```{r}
attributes(map_nj)
```


```{r}

```


A nice clean shortcut here is to use `str(attributes(any_R_object))` which will condense the structure into a short overview:
```{r}
str(attributes(map_nj))
```


#### b. 

What do you think the new attributes mean?

The last five things here are the new attributes. There's an `ndists` argument, a listing of population bounds, a column indicating the population, a column indicating the adjacency, and a column indicating the existing plan.


## 4.

(If you have time, look at this! Don't worry if you can't get through this part.)


#### a.
Plot your `redist_map` with `redist.plot.map`. Use the `plan` argument to point to the existing plan. Set `boundaries = FALSE` to help clean up the plot.

```{r}
p <- redist.plot.map(map_nj, fill = cd_2020, boundaries = FALSE)
ggsave("nj_2020.pdf")
```


#### a. TODO move to a and say this is what they did before

Compare this to plotting just `nj` using the same settings for `redist.plot.map()`

```{r}

```

#### c.
What do you think allows for the cleaner map coloring for the `redist_map`?
